\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-04-06 Drafts and notes/Notes/old_draft.tex
Major change

\begin{thm}\label{thm:wellposed1<p<2} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
\begin{equation*}
    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
\end{equation*}
where
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^{\alpha+1}\right) \varepsilon^{\alpha+1}.
\end{equation*}
\end{thm}
\noindent This is Theorem I.1 in \cite{Lasry1989}. We provide a proof in Appendix with the explicit dependence of $C_\varepsilon$ in terms of $\varepsilon$ for later use, it is useful to note that $\alpha+1 = \frac{1}{p-1}$.

@@

\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{S_0} such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
\end{lem}
\noindent Lemma \ref{lem:max} is a variation of Perron's method. We give a proof in Appendix for the sake of completeness. Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}, we claim that $\{\lambda u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$ and $\lambda$. We have
\begin{equation*}
    u^\varepsilon(x) = \lim_{m\to \infty} u^{\varepsilon}_m(x), \qquad x\in \Omega,
\end{equation*}
 where $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
\begin{equation}\label{e:uepsm}
    \begin{cases}
    \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \;\;\quad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} \tag{PDE$_{\varepsilon,m}$}
\end{equation}
If we assume $\mathrm{(H2)}$ then we can take $C_2 = \Vert f\Vert_{L^\infty(\Omega)}$ and take $\varphi(x) \equiv -\lambda^{-1}C_2$ for $x\in \overline{\Omega}$ as a subsolution to \eqref{e:uepsm}, hence by comparison principle for \eqref{e:uepsm} we have $u^{\varepsilon}_m(x)\geq -\lambda^{-1}C_2$ for all $x\in \overline{\Omega}$, thus as $m\to \infty$ we obtain $u^\varepsilon(x) \geq -\lambda^{-1}C_2$ for all $x\in \Omega$.

The following Theorem says that the large solution $u^\varepsilon$ converges to $u^0$ locally uniformly on $\Omega$ as $\varepsilon\to 0$. We present a simple proof here for the reader's convenience, see also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
\begin{thm}[Vanishing viscosity - Qualitative result]\label{thm:qual} Assume $\mathrm{(A1)}$. Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u^0 \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, $u^0$ solves \eqref{eq:PDE0} and $u^0 \leq u^\varepsilon$ in $\Omega$.
\end{thm}

\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1})
\begin{equation}\label{e:priorie_eps}
    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta
\end{equation}
we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u^0\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u^0$ locally uniformly in $\Omega$. By the stability of viscosity solution we easily deduce that 
\begin{equation}\label{eq:u0int}
   \lambda u^0(x) + H(x,Du^0(x)) = 0 \qquad\text{in}\;\Omega.
\end{equation}
Since $\lambda u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$, we also have $\lambda u^0(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u^0(x)$ and $x\in \Omega$. The coercivity $\mathrm{(H4)}$ implies that there exists $K>0$ such that 
\begin{equation*}
    |u^0(x) - u^0(y)| \leq K \qquad\text{for all}\;x,y\in \Omega.
\end{equation*}
Thus we can extend $u^0$ uniquely to $u^0\in \rmC(\overline{\Omega})$. We will use Lemma \ref{lem:max} to show that $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$. It suffices to show that $u^0\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.

For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, i.e., $v_\delta$ is the unique viscosity solution to
\begin{equation}\label{e:v_v}
    \begin{cases}
    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
    \end{cases}
\end{equation}
As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{v_\delta\}_{\delta>0}$ is uniformly bounded. Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
\begin{equation}\label{eq:vv_eps}
\begin{cases}
    \lambda v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
\end{cases}
\end{equation}
It is well-known that $v^\varepsilon_\delta\to v_\delta$ uniformly on $\overline{\Omega}_\delta$ as $\varepsilon\to 0$.

For all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$. Let $\varepsilon\to 0$ we have $v_\delta \leq u^0$ on $\overline{\Omega}_\delta$.
Let $\delta\rightarrow 0$ we obtain $w\leq u^0$ in $\Omega$, which implies $w\leq u^0$ on $\overline{\Omega}$ since both $w,u^0$ belong to $\rmC(\overline{\Omega})$.
\end{proof}

\subsection{Rate of convergence for first-order equation on nested domain}
For $\delta >0$, let $u\in \rmC(\overline{\Omega})$ and $u_\delta\in \rmC(\overline{\Omega}_\delta)$, respectively, be viscosity state-constraint solutions to 
\begin{equation*}
    \begin{cases}
    \lambda u(x)+H(x,Du(x)) \leq 0 \quad\text{in}\;\Omega,\\
    \lambda u(x)+H(x,Du(x)) \geq 0 \quad\text{on}\;\overline{\Omega},
    \end{cases}\qquad\text{and}\qquad 
    \begin{cases}
    \lambda u_\delta(x)+H(x,Du_\delta(x)) \leq 0 \quad\text{in}\;\Omega_\delta,\\
    \lambda u_\delta(x)+H(x,Du_\delta(x)) \geq 0 \quad\text{on}\;\overline{\Omega}_\delta.
    \end{cases}
\end{equation*} 
It is well-known that $0\leq u_\delta(x) - u(x) \leq C\delta$ for $x\in\overline{\Omega}_\delta$ and this rate is optimal. This can be proved easily by comparison principle when the domain have a scaling structure with $\mathrm{(A3)}$ holds, i.e., $\Omega_\delta = (1-\delta)\Omega$ (see \cite{kim_state-constraint_2020}). We have the following theorem for the general smooth domains.

\begin{thm}\cite{Capuzzo-Dolcetta1990}\label{thm:conv_general} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary. Assume $\mathrm{(H1)}-\mathrm{(H4)}$. 
Then there exists a constant $C$ independent of $\delta$ such that
\begin{equation*}
    0\leq u_\delta(x) - u(x) \leq C\delta \qquad\text{for}\; x\in \overline{\Omega}.
\end{equation*}
\end{thm}
\begin{proof}[Proof of Theorem \ref{thm:conv_general}] Following \cite{Capuzzo-Dolcetta1990}, we construct a $\rmC^2$ diffeomorphism $T:\overline{\Omega}_\delta\to \overline{\Omega}$ that maps $\partial\Omega_\delta$ to $\partial\Omega$ and satisfies
\begin{equation}\label{e:bound_T}
    \sup_{x\in \overline{\Omega}_\delta}\Big(|T(x)-x| + |DT(x) - \mathrm{Id}|\Big) \leq C\delta
\end{equation}
for some constant $C$ independent of $\delta$. Let us define $\tilde{u}_\delta(x) = u_\delta\left(T^{-1}(x)\right)$ for $x\in \overline{\Omega}$. Using $\mathrm{(H4)}$ and \eqref{e:bound_T} we obtain that $\tilde{u}_\delta$ is a viscosity subsolution to
\begin{equation*}
    \lambda \tilde{u}_\delta(x) + H(x,D\tilde{u}_\delta(x))  = C\delta \qquad\text{in}\;\Omega.
\end{equation*}
Therefore by comparison principle $0\leq \tilde{u}_\delta(x) - u(x) \leq C\delta$ on $\overline{\Omega}$, i.e., $0\leq \tilde{u}_\delta(Ty) - u(Ty) \leq C\delta$ on $\overline{\Omega}_\delta$, hence
\begin{equation*}
    0 \leq u_\delta(y) - u(y) \leq u_\delta(y) - u(Ty) + u(Ty) - u(y) \leq C\delta
\end{equation*}
since $u$ is Lipschitz on $\overline{\Omega}$.
\end{proof}

\section{Rate of convergence via the doubling variables method}
\noindent The main result is the following Theorem.
\begin{thm}\label{thm:rate_doubling1} Let $\Omega = B(0,1)$ be the open unit ball in $\mathbb{R}^n$. Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and also $1<p<2$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u^0$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation*}
    0\leq u^\varepsilon(x) - u^0(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{2\sqrt{\varepsilon}}.
\end{equation*}
\end{thm}

\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Let $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ be the state-constraint solution to
\begin{equation}\label{e:PDE_delta}
    \begin{cases}  
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 \qquad\text{in}\; \Omega_\delta\\
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 \qquad\text{on}\; \overline{\Omega}_\delta.
    \end{cases} \tag{PDE$_\delta$}
\end{equation} 
Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later. Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2} and a priori estimate
\begin{equation*}
    \sup_{x\in \overline{\Omega}_\delta} \left(|u_\delta(x)| + |Du_\delta(x)|\right) \leq C_0.
\end{equation*}
We define the auxiliary functional
\begin{align*}
    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|(1+\delta)x-y |^2}{2\sigma^2}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta.
\end{align*}
We split the proof into several steps.
\begin{enumerate}
    \item[1.] Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}_\delta$ such that 
\begin{equation*}
    \max_{\overline{\Omega}\times \overline{\Omega}_\delta} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
\end{equation*}
We can assume that 
\begin{equation}\label{e:ass_delta0}
    d(x_\sigma) < \delta_0
\end{equation}
so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
\item[2.] Since $x_\sigma\in \Omega = B(0,1)$, we have $(1-\delta)x_\sigma \in B(0,1-\delta) = \Omega_\delta$ and by convex combination, for any $\eta\in (0,1)$ we have
\begin{equation*}
    \eta (1-\delta)x_\sigma + (1-\eta)y_\sigma \in \overline{\Omega}_{\delta}.
\end{equation*}
by definition of the maximum of $\Phi^\sigma(x_\sigma,y_\sigma)$ we have
\begin{equation*}
    \Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma\Big(x_\sigma, \eta (1-\delta)x_\sigma + (1-\eta)y_\sigma \Big).
\end{equation*}
That is
\begin{align*}
    &- u_\delta(y_\sigma) - \frac{C_0\big|(1+\delta)x_\sigma - y_\sigma \big|^2}{2\sigma^2} \\
    &\qquad\qquad\geq  - u_\delta\Big(\eta (1-\delta)x_\sigma + (1-\eta)y_\sigma\Big) - \frac{C_0\big|(1+\delta)x_\sigma - \eta (1-\delta)x_\sigma - (1-\eta)y_\sigma \big|^2}{2\sigma^2}.
\end{align*}
Therefore
\begin{align*}
    \frac{C_0}{2\sigma^2}\big|(1+\delta)x_\sigma - y_\sigma \big|^2 &\leq u_\delta\Big(\eta (1-\delta)x_\sigma + (1-\eta)y_\sigma\Big) - u_\delta(y_\sigma) \\
    &\qquad\qquad  + \frac{C_0}{2\sigma^2}\Big|\eta2\delta x_\sigma + (1-\eta)\big((1+\delta)x_\sigma-y_\sigma\big)\Big|^2
\end{align*}

>>>>

\begin{thm}\label{thm:wellposed1<p<2} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
\begin{equation*}
    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1}
\end{equation*}
where
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\alpha = \left(\frac{1}{\alpha}(\alpha+1)^{\alpha+1}\right).
\end{equation*}
\end{thm}
\noindent This is Theorem I.1 in \cite{Lasry1989}. We provide a proof in Appendix with the explicit constant $C_\alpha\varepsilon^{\alpha+1}$ in terms of $\varepsilon$ for later use, it is useful to note that $\alpha+1 = \frac{1}{p-1}$. We also state the following useful results.

\begin{prop}\cite{Lasry1989}\label{prop:u<} Assume the hypothesises of Theorem \ref{thm:wellposed1<p<2}. If $\frac{3}{2}<p<2$ then there exists some constant $C>0$ such that
\begin{equation*}
  \sup_{x\in \Omega} \left|u^\varepsilon(x) - \frac{C_\varepsilon}{d(x)^\alpha}\right| \leq C.
\end{equation*}
\end{prop}

\begin{prop}\cite[Theorem B.3]{alessio_asymptotic_2006}\label{prop:grad} Assume the hypothesises of Theorem \ref{thm:wellposed1<p<2}. The gradient of $u^\varepsilon$ satisfies
\begin{equation*}
    \lim_{d(x)\to 0} \Big( d(x)^{\alpha+1}\nabla u^\varepsilon(x)\Big) = \left(C_\varepsilon \alpha\right) \mathfrak{n}(x_0)
\end{equation*}
where $\mathbf{n}(x_0)$ is the outward unit normal vector to $\Omega$ at $x_0\in \partial\Omega$.
\end{prop}

@@

\begin{lem}\label{lem:max} Let $u\in \rmC(\overline{\Omega})$ be a viscosity subsolution of \eqref{S_0} such that, for all viscosity subsolution $v\in \rmC(\overline{\Omega})$ of \eqref{S_0} one has $v\leq u$ in $\overline{\Omega}$, then $u$ is a viscosity supersolution of \eqref{S_0} on $\overline{\Omega}$.
\end{lem}
\noindent We give a proof of Lemma \ref{lem:max} in Appendix for the sake of completeness.

\begin{lem}\label{lem:lower-bound} Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ be a solution to \eqref{eq:PDEeps}. We have $\{\lambda u^\varepsilon\}_{\varepsilon>0}$ is uniformly bounded from below by a constant independent of $\varepsilon$. Precisely, we have
\begin{equation}\label{e:lower_bound_u_eps}
    \inf_{x\in \Omega} \lambda u^\varepsilon(x) \geq  \inf_{\Omega} f
\end{equation}
and also
\begin{equation}\label{e:lower_bound_u}
    \inf_{x\in \Omega} \lambda u(x) \geq  \inf_{\Omega} f
\end{equation}
\end{lem}
\begin{proof} For $m\in \mathbb{N}$, let $u^{\varepsilon,m}\in \mathrm{C}^2(\Omega)\cap \rmC(\overline{\Omega})$ solves the Drichlet problem
\begin{equation}\label{e:uepsm}
    \begin{cases}
    \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \;\;\quad\quad\qquad\qquad\qquad\qquad u(x) = m &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} \tag{PDE$_{\varepsilon,m}$}
\end{equation}
We have $u^{\varepsilon}_m(x) \to u^\varepsilon(x)$ as $m\to \infty$ in $\Omega$. Let $\varphi(x) \equiv \lambda^{-1} \inf_{\Omega} f$ for $x\in \overline{\Omega}$ then $\varphi(x)$ is a classical subsolution of \eqref{e:uepsm} in $\Omega$ with
\begin{equation*}
    \varphi(x) = \lambda \inf_\Omega f \leq m = u^\varepsilon_m(x) \qquad\text{for}\;x\in \partial\Omega.
\end{equation*}
By comparison principle for the uniformly elliptic equation \eqref{e:uepsm} we have
\begin{equation*}
    \lambda^{-1}\inf_\Omega f \leq u^{\varepsilon}_m(x) \qquad\text{for all}\;x\in \Omega.
\end{equation*}
As $m\to \infty$ we obtain the conclusion \eqref{e:lower_bound_u_eps}. The inequality \eqref{e:lower_bound_u} follows from comparison principle of state-constraint equation \eqref{eq:PDE0} with supersolution $u$ on $\overline{\Omega}$ and subsolution $\varphi(x)$ in $\Omega$.
\end{proof}

We present a simple proof of the convergence $u^\varepsilon \to u$ using Lemma \ref{lem:max} for the reader's convenience, see also \cite[Theorem VII.3]{Capuzzo-Dolcetta1990}.
\begin{thm}[Vanishing viscosity]\label{thm:qual} Assume $\mathrm{(A1)}$. Let $u^\varepsilon$ be the solution to \eqref{eq:PDEeps}, then there exists $u \in \mathrm{C}(\overline{\Omega})$ such that $u^\varepsilon \rightarrow u$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$, $u$ solves \eqref{eq:PDE0} and $u \leq u^\varepsilon$ in $\Omega$.
\end{thm}

\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1})
\begin{equation}\label{e:priorie_eps}
    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta
\end{equation}
we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u$ locally uniformly in $\Omega$. By the stability of viscosity solution we easily deduce that 
\begin{equation}\label{eq:u0int}
   \lambda u(x) + H(x,Du(x)) = 0 \qquad\text{in}\;\Omega.
\end{equation}
Since $\lambda u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$, we also have $\lambda u(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u(x)$ and $x\in \Omega$. The coercivity $\mathrm{(H4)}$ implies that there exists $C_0>0$ such that 
\begin{equation*}
    |u(x) - u(y)| \leq C_0|x-y| \qquad\text{for all}\;x,y\in \Omega.
\end{equation*}
Thus we can extend $u$ uniquely to $u\in \rmC(\overline{\Omega})$. We will use Lemma \ref{lem:max} to show that $u$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$. It suffices to show that $u\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.

For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $u_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, i.e., $u_\delta$ is the unique viscosity solution to
\begin{equation}\label{e:v_v}
    \begin{cases}
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
    \end{cases}
\end{equation}
As $u_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{u_\delta\}_{\delta>0}$ is uniformly bounded. Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
\begin{equation}\label{eq:vv_eps}
\begin{cases}
    \lambda v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
\end{cases}
\end{equation}
It is well-known that $v^\varepsilon_\delta\to v_\delta$ uniformly on $\overline{\Omega}_\delta$ as $\varepsilon\to 0$.

For all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon_\delta \leq u^\varepsilon$ on $\overline{\Omega}_\delta$. Let $\varepsilon\to 0$ we have $v_\delta \leq u$ on $\overline{\Omega}_\delta$.
Let $\delta\rightarrow 0$ we obtain $w\leq u$ in $\Omega$, which implies $w\leq u$ on $\overline{\Omega}$ since both $w,u$ belong to $\rmC(\overline{\Omega})$.
\end{proof}

\subsection{Rate of convergence for first-order equation on nested domain}
For $\delta >0$, we denote $u\in \rmC(\overline{\Omega})$ and $u_\delta\in \rmC(\overline{\Omega}_\delta)$, respectively, viscosity state-constraint solutions to 
\begin{equation*}
    \begin{cases}
    \lambda u(x)+H(x,Du(x)) \leq 0 \quad\text{in}\;\Omega,\\
    \lambda u(x)+H(x,Du(x)) \geq 0 \quad\text{on}\;\overline{\Omega},
    \end{cases}\qquad\text{and}\qquad 
    \begin{cases}
    \lambda u_\delta(x)+H(x,Du_\delta(x)) \leq 0 \quad\text{in}\;\Omega_\delta,\\
    \lambda u_\delta(x)+H(x,Du_\delta(x)) \geq 0 \quad\text{on}\;\overline{\Omega}_\delta.
    \end{cases}
\end{equation*} 
It is well-known that $0\leq u_\delta(x) - u(x) \leq C\delta$ for $x\in\overline{\Omega}_\delta$ and this rate is optimal. This can be proved easily by comparison principle when the domain have a scaling structure with $\mathrm{(A3)}$ holds, i.e., $\Omega_\delta = (1-\delta)\Omega$ (see \cite{kim_state-constraint_2020}). We have the following theorem for the general smooth domains.

\begin{thm}\cite{Capuzzo-Dolcetta1990}\label{thm:conv_general} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary. Assume $\mathrm{(H1)}-\mathrm{(H4)}$. 
Then there exists a constant $C$ independent of $\delta$ such that
\begin{equation*}
    0\leq u_\delta(x) - u(x) \leq C\delta \qquad\text{for}\; x\in \overline{\Omega}.
\end{equation*}
\end{thm}
\begin{proof}[Proof of Theorem \ref{thm:conv_general}] Following \cite{Capuzzo-Dolcetta1990}, we construct a $\rmC^2$ diffeomorphism $T:\overline{\Omega}_\delta\to \overline{\Omega}$ that maps $\partial\Omega_\delta$ to $\partial\Omega$ and satisfies
\begin{equation}\label{e:bound_T}
    \sup_{x\in \overline{\Omega}_\delta}\Big(|T(x)-x| + \big|DT(x) - \mathrm{Id}_{\overline{\Omega}_\delta}(x)\big|\Big) \leq C\delta
\end{equation}
for some constant $C$ independent of $\delta$. Let us define $\tilde{u}_\delta(x) = u_\delta\left(T^{-1}(x)\right)$ for $x\in \overline{\Omega}$. Using $\mathrm{(H4)}$ and \eqref{e:bound_T} we obtain that $\tilde{u}_\delta$ is a viscosity subsolution to
\begin{equation*}
    \lambda \tilde{u}_\delta(x) + H(x,D\tilde{u}_\delta(x))  = C\delta \qquad\text{in}\;\Omega.
\end{equation*}
Therefore by comparison principle $0\leq \tilde{u}_\delta(x) - u(x) \leq C\delta$ on $\overline{\Omega}$, i.e., $0\leq \tilde{u}_\delta(Ty) - u(Ty) \leq C\delta$ on $\overline{\Omega}_\delta$, hence
\begin{equation*}
    0 \leq u_\delta(y) - u(y) \leq u_\delta(y) - u(Ty) + u(Ty) - u(y) \leq C\delta
\end{equation*}
since $u$ is Lipschitz on $\overline{\Omega}$.
\end{proof}

\section{Rate of convergence via the doubling variables method}
\noindent The main result is the following Theorem.

\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(\frac{3}{2},2\right)$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ satisfying $f\geq 0$ in $\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
    0\leq u^\varepsilon(x) - u(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{C\varepsilon^2}.
\end{thm}
\begin{proof} As $f(x)\geq 0$ on $\Omega$, from Lemma \ref{lem:lower-bound} and Theorem \ref{thm:qual} we have 
\begin{equation}\label{e:low}
    u^\varepsilon(x) \geq u(x) \geq 0 \qquad\text{for all}\;x\in \Omega.
From a priori estimate for $u$, we redefine the constant $C_0$ such that
\begin{equation}\label{e:priori}
    \sup_{x\in \overline{\Omega}} \left(\left| u(x)\right| + \left|Du(x)\right|\right) + \Vert \nabla f\Vert_{L^\infty(\Omega)} \leq C_0.
We recall that
\begin{equation}\label{e:behavior_ueps}
    \lim_{d(x)\to 0^+} u^\varepsilon(x)d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1} \qquad\text{where}\qquad \alpha = \frac{2-p}{p-1} \in (0,1) \quad\text{and}\quad C_\alpha := \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
Let 
    G = \left[\left(1+\frac{K_1\delta_0}{\alpha+1}\right)^{\alpha+1} - 1\right]C_\alpha 
then for $\eta = G\varepsilon^{\alpha+1}$, we have 
    \mathcal{W}(x) = \frac{(C_\alpha+G)\varepsilon}{d(x)^\alpha} + \frac{M_\varepsilon}{\lambda}, \qquad x\in \Omega \qquad\text{where}\qquad M_\varepsilon = \sup_{\Omega} f + C\varepsilon^{\alpha+2}.
is a supersolution of \eqref{eq:PDEeps} in $\Omega$. Here $C$ depends only on $K,\alpha,\delta_0$. We therefore can assume $M_\varepsilon\leq \lambda M$ independent of $\varepsilon>0$. Let 
    G_\alpha = \left(1+\frac{K\delta_0}{\alpha+1}\right)^{\alpha+1}C_\alpha
then 
    u^\varepsilon(x) - \frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} \leq M \qquad\text{for all}\; x\in \Omega.
As a consequence, for any $\delta>0$ we have
    u^\varepsilon(x) - (1+\delta) \frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} \leq  M - \delta\frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}}\leq 0 \qquad\text{if}\qquad d(x)< \left(\frac{\delta G_\alpha\varepsilon^{\alpha+1}}{M}\right)^{\frac{1}{\alpha}}.
Let $\delta,\theta,\sigma\in (0,1)$ to be chosen later. We define the following auxiliary functional
    \Phi(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
We split the proof into several steps.
\begin{enumerate}
    \item[1.] From \eqref{e:blows_up} we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, thus for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that 
        \max_{\overline{\Omega}\times \overline{\Omega}} \Phi = \Phi(x_\sigma,y_\sigma).
    We can assume that 
    \begin{equation}\label{e:ass_delta0}
        d(x_\sigma) < \delta_0
    so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ can be easily deduced at the end of the proof.
    \item[2.] From $\Phi(x_\sigma,y_\sigma)\geq \Phi(x_\sigma,x_\sigma)$ we have
        & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_0|x_\sigma-x_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}.
    Therefore
